
## Data aggregation

Table \@ref(tab:sourcestable) shows the data sources used and how many records were retrieved from each source by envOcc [@RN4605].

```{r sourcestable}
  
bio_all_info |> 
  dplyr::mutate('date retrieved' = as.Date(modification_time)) |> 
  dplyr::select("name" = data_name_use, "description" = desc, 'date retrieved', records, ref) |>
  env_kable_extra(format.args = list(big.mark = ",")
                  , caption = "Data sources contributing to the aggregated dataset."
                  , height = "500px"
                  )

```

## Summary of cleaning results {#cleanresult}

Table \@ref(tab:cleanResult) shows the number of taxa, records, visits and sites as the data moved through the cleaning process. At the end of the cleaning process there were `r format(min(clean_summary$taxa), big.mark = ",")` taxa from `r format(min(clean_summary$sites), big.mark = ",")` sites with `r format(min(clean_summary$records), big.mark = ",")` records.

See the [appendices](#surveybins) Table \@ref(tab:surveysTidy) for surveys contributing bins to further analysis after all the data cleaning, filtering and tidying.

```{r cleanResult}

clean_summary |>
  dplyr::select(clean, desc, taxa, records, visits, sites) |>
  env_kable_extra(caption = "Summary of the cleaning process"
                  , format.args = list(big.mark = ",")
                  )

```
