
## Environmental data {#envdata}

To help predict the occurrence data a total of `r numbers2words(nrow(env_df_info))` layers were generated  from `r numbers2words(length(unique(env_df_info$source)))` data sources. Not all layers were used in the model for each taxa (see [explanatory variables](#expvar)).

In order to smooth over year-to-year fluctuations in the environmental data, each layer was generated by a function applied over the `r readr::parse_number(envFunc::extract_scale("fine", scales = here::here("settings", "scales.yaml"))$grain$res_x)`
`r envTargets::extract_temporal_grain(envFunc::extract_scale("fine", scales = here::here("settings", "scales.yaml"))$grain$res_x)` period starting on `r names(which.max(table(env_df$start_date)))`. Some layers had no temporal component. These layers are labelled as 'static'.

Table \@ref(tab:envVariables) lists the source, collection, and layer along with any function applied to all images in the original collection that intersected the geographic and temporal extent. The function was applied to any cells in the original collection that had their cell centres overlapping any of the `r envFunc::extract_scale("fine", scales = here::here("settings", "scales.yaml"))$grain$res_y` m cells in a base grid created as a template for all resulting layers.

```{r envVariables}

df <- env_df_info

df$source <- kableExtra::cell_spec(df$source, "html", link = df$source_url)
df$collection <- kableExtra::cell_spec(df$collection, "html", link = df$data_ref)

df |>
  dplyr::select(source, collection, layer, period, func, start_date) |>
  env_kable_extra(caption = "Environmental variables: source, collection, and layer along with any function applied to the period over which layers were summarised and the start date of the period."
                  , escape = FALSE
                  , height = "500px"
                  )

```

```{r envVarText, results = "asis"}

envRaster::knit_env_layers(ids = unique(env_df_info$source))

```
